A Flux Scale for Southern Hemisphere 21cm EoR Experiments

### 2013-06-19 ms.tex
Jonnie's edits of overview section
Signed-off-by: Danny Jacobs <daniel.c.jacobs@asu.edu>

\subsection{Data Processing Overview}
\label{sec:data_overview}
The spectra reported here are measured by beam-forming ---phasing the visibilities to
the target location and summing over baselines to produce a spectral time series of perceived flux $S_p$,
which is given by the true source flux, $S$, illuminated by the true beam pattern $B$, according to
\begin{equation}
S_p=B(t)S.
\end{equation}
The spectrum is then isolated
from neighboring sources by filtering and averaged in the time domain.  This time-average is 
weighted by a model of PAPER's primary beam response ($B_M$). As the perceived flux is already weighted once by the true beam $B$ this weighted sum is an effective approximation of inverse-variance weighting \citep{Pober:2012p8800}. 
\begin{align}
S_\textrm{est} &= \frac{\sum_t B(t)_M S_p}{\sum_t B(t)^2_M} \nonumber \\ 
&= \frac{\sum_t B(t)_M B(t)}{\sum_t B(t)^2_M} S  \nonumber \\
&\equiv g(\delta) S  \label{eq:g}
\end{align}
The net time integrated, weighted beam response $g$ is purely a function of declination $\delta$.The rate at which this factor
changes with declination defines maximum declination distance we can observe from our calibrator. 
To simulate this affect we we multiplied a measurement of the primary beam \citep{Pober:2012p8800}
by electromagnetic simulations \citep{Parsons:2010p6757} and find that $g$ 
diverges slowly with declination, with a maximum of 10\% over 5\arcdeg{} of declination range, though most are less. Thus, to first order,
calibration to a single declination will remove most of the variation with declination.
We estimate this spectral dependent $g$ at a reference declination of 41\arcdeg{}36\arcmin{}  using (J2331-416) fitting a spectral index model to the
 catalog data points below 2GHz. This levels the bandpass due to spectral dependence  of the primary bean 
 and puts all the sources on approximately the same flux scale.  
 Finally we average the spectra from a resolution of 400kHz to 10MHz bins, adding the individual errors in quadrature
 for our uncertainty.

@@

First, we remove known RFI transmission bands and analog filter edges, and then
flag outliers at 6$\sigma$ to remove RFI events.  Next, we suppress sky-like
emission by applying a DDR filter to remove delays and delay-rates within the
horizon limit of a 300-m baseline (the maximum length of any PAPER baseline).
We derive a second set of RFI flags by masking 4$\sigma$ outliers in these
residuals and apply these flags back to the unfiltered data.  Finally, we
compress the data by applying a DDR filter preserving emission within the
horizon limit of a 300-m baseline, deconvolving to suppress flagging artifacts,
and down-sampling the result in time/frequency domain to the critical Nyquist
rate of the DDR filter.  The result is that the 2048 original frequency
channels become 203, and the 60 original time samples per 10-minute file become
14.

>>>>

\subsection{Analysis Overview}
\label{sec:data_overview}
The spectra reported here are measured by beam-forming --- phasing the visibilities to
the target location and summing over baselines to produce a spectral time series of ``perceived'' flux $S_p$.
We define a perceived flux as the true source flux density, $S$, illuminated by the true beam pattern $B$:
\begin{equation}
S_p=B(t)S,
\end{equation}
where $B$ is a function of time because the observations are taken as a drift
scan.
The desired source spectrum is then isolated
from neighboring sources by filtering.%XXX what kind of filtering?
We then average the spectrum in the time domain,
weighting by a model of PAPER's primary beam response ($B_M$); as the perceived flux is already weighted once by the true beam $B$, this weighted sum is an effective approximation of inverse-variance weighting \citep{Pober:2012p8800}.
Mathematically, our estimated source flux density is given by: 
\begin{align}
S_\textrm{est} &= \frac{\sum_t B(t)_M S_p}{\sum_t B(t)^2_M} \nonumber \\ 
&= \frac{\sum_t B(t)_M B(t)}{\sum_t B(t)^2_M} S  \nonumber \\
&\equiv g(\delta) S  \label{eq:g},
\end{align}
where the subscript $M$ indicates a model beam, and the $S$ without subscript is the true flux density of the source.
The net time integrated, weighted beam response $g$ is purely a function of declination $\delta$.  The rate at which this factor
changes with declination defines the declination range over which our calibrator source can be used to set the gain scale of the observations.
To simulate this affect we we multiplied a measurement of the primary beam \citep{Pober:2012p8800}
by electromagnetic simulations \citep{Parsons:2010p6757} and find that $g$ 
diverges slowly with declination, with a maximum of 10\% over 5\arcdeg{} of declination range, though most are less. %XXX most what are less?
Thus, to first order,
we can use our calibrator source to calibrate sources within 5\arcdeg{} of declination and remove most of the variation with declination.
We estimate this spectral dependent $g$ at a reference declination of 41\arcdeg{}36\arcmin{} using (J2331-416), fitting a spectral index model to the
 catalog data points below 2GHz. This levels the bandpass due to spectral dependence of the primary beam, and allows us to place our measured source flux
estimates
on approximately the same flux scale.  
 Finally we average the spectra from a resolution of 400kHz to 10MHz bins, adding the individual errors in quadrature
 for our uncertainty.

@@

First, we remove known RFI transmission bands and analog filter edges, and then
flag outliers in the frequency and time derivative at 6$\sigma$ to remove RFI events.  Next, we suppress sky-like
emission by applying a DDR filter to remove delays and delay-rates within the
horizon limit of a 300-m baseline (the maximum length of any PAPER baseline).
We derive a second set of RFI flags by masking 4$\sigma$ outliers in these
residuals and apply these flags back to the unfiltered data.  Finally, we
compress the data by applying a DDR filter preserving emission within the
horizon limit of a 300-m baseline, deconvolving to suppress flagging artifacts,
and down-sampling the result in time/frequency domain to the critical Nyquist
rate of the DDR filter.  The result is that the 2048 original frequency
channels become 203, and the 60 original time samples per 10-minute file become
14.
